Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-26 paper/paper.tex
Fix typo.;

We would also like to incorporate latent factors into our model.
Latent factor techniques, such as the those presented in \cite{Koren2009}, have
become very popular since the Netflix Challenge and have proved to be better for
predicting user-item rating than classical CF. One experiment would be to
construct a new $TrueSimLatent$ based on the similarity of two items in 
latent factor space. Then we could apply both of the approaches in this
paper analagously in latent factor space. Another idea is to use latent factors 
as a new input to a model for predicting $TrueSimRand$ or $TrueSimPref$.

>>>>

We would also like to incorporate latent factors into our model.
Latent factor techniques, such as those presented in \cite{Koren2009}, have
become very popular since the Netflix Challenge and have proved to be better for
predicting user-item rating than classical CF. One experiment would be to
construct a new $TrueSimLatent$ based on the similarity of two items in 
latent factor space. Then we could apply both of the approaches in this
paper analagously in latent factor space. Another idea is to use latent factors 
as a new input to a model for predicting $TrueSimRand$ or $TrueSimPref$.
